Transforming Trash as an Artistic Act

### 2015-12-29 chapter2_reduced.tex
Chapter 2 review
Former-commit-id: de9640209bade5dc3b51e32502a643f004e1026b
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88

\chapter{Trash in Culture and Theory}

% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych, http://priscilauppal.ca/books/alphabet-city/
\epigraph{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}

@@

%
%
\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. Disposable items with the help of industrialization can be produced easily. Mass production. Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs. wipes, glass vs. paper cup). Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontologyh}.}

>>>>

\chapter{TRASH IN CULTURE AND THEORY}

% Epigraph
\begin{singlespace}
% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych, http://priscilauppal.ca/books/alphabet-city/
\epigraph{Anger is nothing compared to garbage:\\Garbage eats anger for breakfast.\\It eats all of us in the end.}{\hfill---Priscilla Uppal, \quotes{Uncle Fernando’s Garbage Triptych}}
\end{singlespace}

@@

%
%
\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. Disposable items with the help of industrialization can be produced easily. Mass production. Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs. wipes, glass vs. paper cup). Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontology}.}

### 2015-12-29 drafts.tex
thesis format
Former-commit-id: 4c193566fa7da80661a70ce4067ea75d9e65ec88

>>>>

My work relation with the other works.

(My work needs to be considered in the context of art. I need to focus on the notebooks establish with art.)

sanki çöplerden bir şeyler yapmak bir şeyleri ispatlamak gibi gözüküyor. Ya da gene bir yetenek gibi gözüküyor. Bulunmaz kumaş misali. Yok abi kimsenin başaramadığı şeyi başarıyorum gibi bir şey yok. Ben ilgilinilmeyenle ilgileniyorum.
